Combined Task and Motion Planner through an Interface Layer

### 2015-04-17 documentation/draft.tex
initial pass of algorithm discussion in tutorial

-zoom into features, explain how they work on a technical level

-enough understanding to derive + implement algorithm on their own

things to talk about:

@@

In the TryRefine subroutine, the interface layer attempts to find motion plans corresponding to the various actions.  
It has two modes: error free and partial trajectory.  
In error free mode, it performs backtracking search to try to find a full plan from start to finish.  
In partial trajectory mode, it goes as far as it can, but when it finds an infeasible motion plan, it returns the step at which it failed.  
In addition to returning the failed step, it returns the cause of the errors.  
The function MPErrs removes various objects from the environment until it find a plan which succeeds.  
It then marks all of those objects which were removed as blocking objects.

NOTE TO BIANCA: include paragraph about how we utilize pose generators here

there will be another couple paragraphs here extending this

\subsection{API and Interfaces}

Alex should write this section, probably mostly the same as the stuff he's writing for the readme/etc.

>>>>

In this section, we discuss the key insight of the original paper: the ability to avoid discretization by representing continuous variables symbolically via references.  
We also discuss the pose generators which propose real-world instantiations of these references.  
Finally, we walk through the algorithm in detail.

@@

In the TryRefine subroutine, the interface layer attempts to find motion plans corresponding to the various actions.  
It has two modes: error free and partial trajectory.  
In error free mode, it performs backtracking search to try to find a full plan from start to finish.  
The backtracking search is over possible pose instantiations: since some poses may be infeasible and since previous choices may affect future choices, the backtracking search iterates over all possible poses in order to find a full solution if a full solution exists.

In partial trajectory mode, TryRefine goes as far as it can, but when it finds an infeasible motion plan for some action, it returns the step at which it failed.  
In addition to returning the failed step, it returns the cause of the errors.  
The function MPErrs removes various objects from the environment until it find a plan which succeeds.  
It then marks all of those objects which were removed as blocking objects.

To find the blocking objects, we start by iterating through a randomized list of the objects.  We continue removing objects until we find a successful motion plan.  
We will eventually find a successful motion plan since if there are no other objects in the world, the motion should succeed.  
After we find this possible list of removed objects, we iterate through all of the objects we removed.  
We attempt to add these objects in one by one, leaving added in all of those which don't obstruct our found motion plan.  
This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
However, for this set of this set of objects, no object can be added back in without obstructing the motion plan.

As described above in Algorithm 1, once the list of blocking objects is returned, the interface layer updates the state and attempts to replan from there.
